Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
standardize Lazy D and Lazy UD font

\newcommand{\lazyUD}{$\mathtt{Lazy UD}$}
\newcommand{\lazyD}{$\mathtt{Lazy D}$}
\newcommand{\eager}{$\mathtt{Eager}$}

@@

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. We are unaware of any 
strong argument favoring D or UD, so we study both \lazyD\ and \lazyUD.
\todo[inline]{Why do we need to explain why both LD and LUD? -KC
  \\---\\
Because the paper includes both. -JS
\\---\\
Fixed. -KC}

>>>>

\newcommand{\lazyUD}{Lazy\;UD}
\newcommand{\lazyD}{Lazy\;D}

@@

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that eager strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. We are unaware of any 
strong argument favoring D or UD, so we study both \lazyD\ and \lazyUD.
\todo[inline]{Why do we need to explain why both LD and LUD? -KC
  \\---\\
Because the paper includes both. -JS
\\---\\
Fixed. -KC}
